Designing a Search for the BBC

### 2014-02-06 paper.tex
Capitalised heading.
Abbreviated "figure" to "Fig." as advised by format guide.

\documentclass{llncs}

@@

\title{Designing a Search for the BBC}
\author{Ross Fenning}
\institute{BBC}

@@

\tableofcontents

@@

The overall design objective will be to create an initial proposal for a
search application to drive the missing components within the holistic
system depicted in figure~\ref{rich-picture}. Some subsystems already
exist, e.g. for journalists to write news articles and publish them on the
BBC News website, but for the purposes of this design exercise, we will
assume no existing application to drive a search-based discovery of
those websites.

@@

\subsection{Use cases}

From the rich picture in figure~\ref{rich-picture}, we can attempt to
extract the activities that are clearly within the remit of a search
application. For example, the ability for editorial staff to manage
the content of the search indexes sounds like a feature the search
application would provide. Conversely, television actors and other
contributors to a programme are likely to interact only within a television
production subsystem with a producer or content editor being responsible
for publishing information about the final production's broadcast and
availability for streaming online.

@@

Having extracted the activities that appear to pertain to the
search application directly (and the actors involved in those activities),
we can produce the use case UML diagram shown in figure~\ref{use-case}.

@@

Figure~\ref{sequence-producer}
shows how a TV producer indirectly interacts with search by providing
information that ultimately ends up in the search indexes and
figure~\ref{sequence-user} shows a sequence diagram defining a user
interacting with the search system

The key design decision in figure~\ref{sequence-producer} is the use of
asynchronous messages only. A non-blocking set of interactions such as
publish-subscribe \citep{hohpe2004enterprise} is a good way to decouple
systems that produce and store progamme information from the search
application systems. If the systems surrounding the programmes database
can be built a \emph{channel adapter} \citep{hohpe2004enterprise} to integrate
it to a messaging system, then the search indexes can receive changes to
information without TV producers, journalists, content
editors, etc. even being aware this is happening.

Note in figure~\ref{sequence-user} that while the search indexes
will contain representations of content
from several source systems, the intention shown is that richer information
about the domain model will not be held in the search indexes. This goes
along with the principle of separation of concerns \citep{dijkstra1982role}
in that the search index component can focus on optimising its data
structures around retrieval. This kind of modularity also allows source
systems maintained by other teams to take the responsibility of the
accuracy of the information, which fits in with the wider holistic view
of the system: the volume of information involved requires that
separate teams are responsible for the accuracy of their data.

@@

One solution to this in modern web application design is to
push the lazy loading into the web browser using AJAX. \citep{garrett2005ajax}
Such a solution is depicted in figure~\ref{sequence-ajax}. Whilst
this still requires just as many calls to backend services --
perhaps even more complexity as the calls are going through
more layers -- it can give a user experience that appears more responsive.

@@

It has been expressed already that a BBC-wide search application
is going to have to index, retrieve and display a diverse set of
information. Parts of the application might well want to incorporate
a domain model \citep{fowler2002patterns} so as to understand how
to perform each of these actions against each possible item
the search application could return as a search result. A maximal
model is shown in figure~\ref{model} that attempts to capture
a good proportion of the content and concepts the BBC has
been attempting to model over several years. This model is
an aggregate of individual ontologies developed for specific purposes,
but given the search application has to provide the discovery for
the full set of this information, it is not unreasonable that
a search application would have a domain model that covers the totality.

@@

The behaviour of the query web application in figure~\ref{sequence-user}
is defined with a hard line
taken on keeping the information stored in the indexes to a minimum.
At a basic level, this is not unlike a \emph{content enricher} pattern
\citep{hohpe2004enterprise} whereby the search application
business layer enriches the stubs in the indexes with information
the source system (the index) simply does not have. At a more purist
extreme, this could follow a \emph{claim check} pattern where
the index returns only globally-unique identifiers for the matching
items and makes no attempt to present any other knowledge about them
(and thus avoids any synchronisation issues if an item is updated at
source).

The latter pattern fully decouples the search indexes from any
deeper information -- leaving that responsbility to appropriate
source system -- but means that the raw, stub results are near-useless
to an end user. This makes the AJAX-based alternative approach
in figure~\ref{sequence-ajax}
less of a desirable option (would a user really be presented a list
of URIs while some Javascript code replaces them one by one with
actual information?). Given the AJAX-driven behaviour still appears
desirable in terms of responsiveness, it would seem that some trade-off
would need to happen in terms of what the indexes store as additional
information.

These decisions relate to how the system would implement the data model
in figure~\ref{model}. The onotology described is an aggregation
of several efforts by Raimond \citep{raimond2009bbc}, Rayfield
\citep{rayfield2011bbc} and others -- along with some additional work
to join them together -- to represent the wealth of
information with which the BBC deals. It could be argued both that
a search application that \emph{understands} this diversity of
content must reflect it in its domain model but that a search
application that is \emph{coupled} to the individual ontologies
in this way is brittle with regard to changes therein. Duplication
would only harm maintainability.

Thus the domain model given in figure~\ref{model} should only serve
as a communication artefact that leads to further development of
a domain model more suitable to the needs of the search application
without the burden of maintaining more than is necessary. The use
of \emph{subtype polymorphism} \citep{booch2007object} is likely
to be key to ensure the search domain model contains only the APIs
it needs. For example, does the search application have a need
to differentiate between a \emph{NewsItem} and a \emph{BlogPost}
for the purposes of displaying the search result's title? If the
CreativeWork top-level class has a title property, then the domain
model so far to enable that one behaviour needs only one class!

>>>>

\documentclass[oribibl]{llncs}

@@

\title{Designing a Search for the BBC}
\author{Ross Fenning\inst{1}}
\institute{BBC \email{Ross.Fenning@bbc.co.uk}}

@@

\begin{abstract}

\end{abstract}

@@

The overall design objective will be to create an initial proposal for a
search application to drive the missing components within the holistic
system depicted in Fig.~\ref{rich-picture}. Some subsystems already
exist, e.g. for journalists to write news articles and publish them on the
BBC News website, but for the purposes of this design exercise, we will
assume no existing application to drive a search-based discovery of
those websites.

@@

\subsection{Use Cases}

From the rich picture in Fig.~\ref{rich-picture}, we can attempt to
extract the activities that are clearly within the remit of a search
application. For example, the ability for editorial staff to manage
the content of the search indexes sounds like a feature the search
application would provide. Conversely, television actors and other
contributors to a programme are likely to interact only within a television
production subsystem with a producer or content editor being responsible
for publishing information about the final production's broadcast and
availability for streaming online.

@@

Having extracted the activities that appear to pertain to the
search application directly (and the actors involved in those activities),
we can produce the use case UML diagram shown in Fig.~\ref{use-case}.

@@

Figure~\ref{sequence-producer}
shows how a TV producer indirectly interacts with search by providing
information that ultimately ends up in the search indexes and
Fig.~\ref{sequence-user} shows a sequence diagram defining a user
interacting with the search system

The key design decision in Fig.~\ref{sequence-producer} is the use of
asynchronous messages only. A non-blocking set of interactions such as
publish-subscribe \citep{hohpe2004enterprise} is a good way to decouple
systems that produce and store progamme information from the search
application systems. If the systems surrounding the programmes database
can be built a \emph{channel adapter} \citep{hohpe2004enterprise} to integrate
it to a messaging system, then the search indexes can receive changes to
information without TV producers, journalists, content
editors, etc. even being aware this is happening.

Note in Fig.~\ref{sequence-user} that while the search indexes
will contain representations of content
from several source systems, the intention shown is that richer information
about the domain model will not be held in the search indexes. This goes
along with the principle of separation of concerns \citep{dijkstra1982role}
in that the search index component can focus on optimising its data
structures around retrieval. This kind of modularity also allows source
systems maintained by other teams to take the responsibility of the
accuracy of the information, which fits in with the wider holistic view
of the system: the volume of information involved requires that
separate teams are responsible for the accuracy of their data.

@@

One solution to this in modern web application design is to
push the lazy loading into the web browser using AJAX. \citep{garrett2005ajax}
Such a solution is depicted in Fig.~\ref{sequence-ajax}. Whilst
this still requires just as many calls to backend services --
perhaps even more complexity as the calls are going through
more layers -- it can give a user experience that appears more responsive.

@@

It has been expressed already that a BBC-wide search application
is going to have to index, retrieve and display a diverse set of
information. Parts of the application might well want to incorporate
a domain model \citep{fowler2002patterns} so as to understand how
to perform each of these actions against each possible item
the search application could return as a search result. A maximal
model is shown in Fig.~\ref{model} that attempts to capture
a good proportion of the content and concepts the BBC has
been attempting to model over several years. This model is
an aggregate of individual ontologies developed for specific purposes,
but given the search application has to provide the discovery for
the full set of this information, it is not unreasonable that
a search application would have a domain model that covers the totality.

@@

The behaviour of the query web application in Fig.~\ref{sequence-user}
is defined with a hard line
taken on keeping the information stored in the indexes to a minimum.
At a basic level, this is not unlike a \emph{content enricher} pattern
\citep{hohpe2004enterprise} whereby the search application
business layer enriches the stubs in the indexes with information
the source system (the index) simply does not have. At a more purist
extreme, this could follow a \emph{claim check} pattern where
the index returns only globally-unique identifiers for the matching
items and makes no attempt to present any other knowledge about them
(and thus avoids any synchronisation issues if an item is updated at
source).

The latter pattern fully decouples the search indexes from any
deeper information -- leaving that responsbility to appropriate
source system -- but means that the raw, stub results are near-useless
to an end user. This makes the AJAX-based alternative approach
in Fig.~\ref{sequence-ajax}
less of a desirable option (would a user really be presented a list
of URIs while some Javascript code replaces them one by one with
actual information?). Given the AJAX-driven behaviour still appears
desirable in terms of responsiveness, it would seem that some trade-off
would need to happen in terms of what the indexes store as additional
information.

These decisions relate to how the system would implement the data model
in Fig.~\ref{model}. The onotology described is an aggregation
of several efforts by Raimond \citep{raimond2009bbc}, Rayfield
\citep{rayfield2011bbc} and others -- along with some additional work
to join them together -- to represent the wealth of
information with which the BBC deals. It could be argued both that
a search application that \emph{understands} this diversity of
content must reflect it in its domain model but that a search
application that is \emph{coupled} to the individual ontologies
in this way is brittle with regard to changes therein. Duplication
would only harm maintainability.

Thus the domain model given in Fig.~\ref{model} should only serve
as a communication artefact that leads to further development of
a domain model more suitable to the needs of the search application
without the burden of maintaining more than is necessary. The use
of \emph{subtype polymorphism} \citep{booch2007object} is likely
to be key to ensure the search domain model contains only the APIs
it needs. For example, does the search application have a need
to differentiate between a \emph{NewsItem} and a \emph{BlogPost}
for the purposes of displaying the search result's title? If the
CreativeWork top-level class has a title property, then the domain
model so far to enable that one behaviour needs only one class!
